Network Management Experiences

### 2024-10-29 paper.tex
updated template

\title{Managing IoT Devices with LwM2M}

\author{John Doe}
\email{john.doeericsson.com}
\orcid{0009-0008-2864-4269}
\affiliation{%
  \institution{Ericsson}
  \city{Jorvas}
  \country{Finland}
}

@@

The rapid evolution of network management protocols ...

This paper references key protocols such as NMDA \cite{rfc8342}, NETCONF \cite{rfc6241}, and SNMP \cite{rfc3411} to explore advancements in network management.

@@

@@

@@

% Maybe GenAI and Intents?
% Maybe AI?
% RESTCONF/CORECONF (compression YANG/CBOR)

>>>>

\title{Network Management Experiences}

\author{J. Doe}
\email{j.doe@ericsson.com}
\orcid{0009-0008-2864-4269}
\affiliation{%
  \institution{Ericsson}
  \city{Jorvas}
  \country{Finland}
}

\author{J. Doe}
\email{j.doe@ericsson.com}
\orcid{0009-0008-2864-4269}
\affiliation{%
  \institution{Ericsson}
  \city{Jorvas}
  \country{Finland}
}

\author{J. Doe}
\email{j.doe@ericsson.com}
\orcid{0009-0008-2864-4269}
\affiliation{%
  \institution{Ericsson}
  \city{Jorvas}
  \country{Finland}
}

@@

The IAB workshop on the Next Era of Network Management Operations (NEMOPS) aims to foster dialogue between network operators and protocol developers, guiding the IETF in evolving network management protocols. This initiative seeks to evaluate past achievements and outline future requirements for network management operations.

In this paper we introduce a cloud-native transport automation software solution designed to machine learning and open standards for advanced analytics and automation across microwave, IP, and optical fronthaul networks. The goal being to facilitate communication service providers the automation of their network operations, optimizing network performance, reducing costs, and enhancing end-user experiences.

@@

Depending on how deep we can get on what we can say at IETF, we may scope the paper accordingly

@@

% Network Automation
% Network Analytics/Visibility
% Maybe ML?
% RESTCONF/CORECONF (compression YANG/CBOR)

We use protocols such as NMDA \cite{rfc8342}, NETCONF \cite{rfc6241}, and SNMP \cite{rfc3411} to ...

@@

% Maybe GenAI and Intents?
% More standard interfaces?
% More closed-loop Automation
% Workflow Programmability and Network APIs (Ericsson message)
